---
title: "TextAnalysis_Final_Project"
author: "Hatice Banu Yildirim"
date: "2025-06-15"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    css: styles.css
  pdf_document:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---

```{css, echo=FALSE}
.challenge-box {
  padding: 1em;
  margin: 1em 0;
  border-left: 5px solid #2c3e50;
  background-color: #f8f9fa;
}

.tip-box {
  padding: 1em;
  margin: 1em 0;
  border-left: 5px solid #27ae60;
  background-color: #f8f9fa;
}

.section-break {
  text-align: center;
  margin: 2em 0;
}
```

# Introduction

Project Title: Sentiment and Topic Analysis of Financial Headlines —
Using Traditional Methods on Financial PhraseBank

This project explores financial news headlines using a full text
analysis pipeline that integrates both unsupervised and supervised
natural language processing (NLP) methods. Our goal is to extract
meaningful insights from text data and evaluate the predictive
performance of classification models in identifying sentiment.

### *Research Objective*

Identify and visualize dominant themes using topic models (LDA, STM)
Explore word associations using word embeddings and t-SNE Train and
compare supervised models (Naive Bayes, XGBoost, Random Forest) for
sentiment classification Assess performance using metrics like accuracy,
precision, recall, and confusion matrix Optionally explore how Large
Language Models (LLMs) can improve classification in ambiguous cases

# Data Overview

Financial PhraseBank \~4,800 English-language financial news headlines
Sentiment labels: positive, negative, neutral Expert-annotated by
finance professionals Balanced across different sentiment categories
Ideal for both topic modeling and sentiment classification

# 1. Project Structure and Methodology

##Setup Chunk

```{r setup, message=FALSE, warning=FALSE}
# Install required packages (only needed once)
# Commented out to prevent reinstallation every time
# install.packages(c("stm", "readr", "tidyverse", "ggplot2", "SnowballC", "tm", "dplyr", "stringr", "tidyr", "slam", "rsample", "textrecipes", "discrim", "tidymodels", "scales", "LiblineaR", "parsnip", "naivebayes", "DMwR", "ranger", "xgboost", "readxl"), repos = "https://cran.rstudio.com/")

# Load libraries
library(readr)         # Read CSV data
library(dplyr)         # Data manipulation
library(tm)            # Text mining
library(quanteda)      # Tokenization and DFM
library(syuzhet)       # Sentiment analysis
library(ggplot2)       # Visualization
library(wordcloud)     # Word clouds
library(RColorBrewer)  # Color palettes
library(stringr)       # String operations
library(topicmodels)   # LDA topic modeling
library(stm)           # Structural Topic Modeling
library(text2vec)      # GloVe and t-SNE
library(Rtsne)         # t-SNE visualization
library(tidymodels)    # Modeling framework
library(textrecipes)   # Text preprocessing
library(discrim)       # Naive Bayes model
library(xgboost)       # Boosted tree model
library(yardstick)     # Evaluation metrics
library(tidytext)
library(Rtsne)
library(ggrepel)
```

# Preprocessing

# Corpus Construction

```{r load-data, message=FALSE, warning=FALSE}
data <- read_csv("~/Desktop/text_analysis/data/raw/all-data.csv",
                 col_names = FALSE,
                 locale = locale(encoding = "ISO-8859-1"))
colnames(data) <- c("label", "text")
```

## Cleaning and Tokenization

```{r}
data$text_clean <- tolower(data$text)
data$text_clean <- removePunctuation(data$text_clean)
data$text_clean <- removeNumbers(data$text_clean)
data$text_clean <- removeWords(data$text_clean, stopwords("en"))
corp <- corpus(data$text_clean)
tokens_clean <- tokens(corp,
                       remove_punct = TRUE,
                       remove_numbers = TRUE,
                       remove_symbols = TRUE) %>%
  tokens_tolower() %>%
  tokens_remove(stopwords("en"))
```

## Stemming/Lemmatization

```{r}
# Note: In this implementation, stemming/lemmatization is not manually applied.
# However, stemming is later included automatically in `textProcessor()` (STM section).
# Since this dataset consists of short financial texts, stemming is preferred over lemmatization
# to reduce sparsity and generalize similar terms (e.g., "profits", "profitable" → "profit")
```

## Exploration

```{r}

# Document length distribution
data$doc_length <- ntoken(tokens_clean)
hist(data$doc_length,
     breaks = 50,
     col = "lightgreen",
     main = "Document Length Distribution",
     xlab = "Number of Tokens")

#The histogram above shows the distribution of document lengths in terms of the number of tokens per document. Most documents contain between 5 and 20 tokens, with a peak around 10 tokens. This suggests that the dataset consists of relatively short texts, which could limit the depth of topic modeling but may be suitable for classification tasks like sentiment analysis.

# Wordcloud

dfm_mat <- dfm(tokens_clean)
top_words <- topfeatures(dfm_mat, 100)
set.seed(123)
wordcloud(words = names(top_words),
          freq = top_words,
          max.words = 100,
          colors = brewer.pal(8, "Dark2"),
          random.order = FALSE)

#The word cloud displays the most frequent terms in the corpus after stopword removal. Prominent terms like "eur", "company", "profit", and "sales" suggest that the dataset primarily contains financial and business-related news. These insights help align the research focus toward economic sentiment or topic clustering in business reporting

#Sentiment Score Distribution

sentiment_scores <- get_sentiment(data$text_clean)
hist(sentiment_scores,
     main = "Sentiment Score Distribution",
     xlab = "Sentiment Score",
     col = "lightblue")

#The sentiment score distribution appears to be slightly right-skewed, with a concentration of scores around neutral (0). This indicates that most documents in the dataset express neutral to mildly positive sentiment. This is consistent with financial reporting, which often strives for objective or neutral language.

```

# 1.2 Unsupervised Analysis (e.g., Topic Modeling, Clustering)

## LDA Model

```{r}
text_corpus <- Corpus(VectorSource(data$text_clean))
dtm <- DocumentTermMatrix(text_corpus, control = list(wordLengths = c(3, Inf)))
row_totals <- apply(dtm, 1, sum)
dtm_clean <- dtm[row_totals > 0, ]

# LDA Model(5 topics)

lda_model <- LDA(dtm_clean, k = 5, control = list(seed = 1234))
topics <- tidy(lda_model, matrix = "beta")

# Top 10 terms per topic
top_terms <- topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ggplot(top_terms, aes(x = reorder(term, beta), y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  labs(title = "Top Terms in Each Topic (LDA)", x = "Term", y = "Beta")

```

**Interpretation of LDA Results**

The Latent Dirichlet Allocation (LDA) model was applied with k = 5
topics on the cleaned document-term matrix. The plot above displays the
top 10 terms for each topic, ranked by their beta values, which
represent the probability of a term appearing in a given topic.

-   Topic 1 appears to be focused on financial and corporate terms
    related to Finnish businesses, including words such as “eur,”
    “company,” “finland,” “million,” and “net.”

-   Topic 2 also centers around corporate finance, highlighting words
    like “profit,” “shares,” “operating,” and “year,” indicating an
    emphasis on firm-level financial performance and earnings.

-   Topic 3 shows a distinct focus on future-oriented language (e.g.,
    “will,” “services,” “percent”), possibly capturing forward-looking
    statements and corporate outlooks.

-   Topic 4 contains similar financial vocabulary (“sales,” “operating,”
    “quarter,” and “group”), potentially reflecting quarterly earnings
    reports and sales activity.

-   Topic 5 is notable for including brand-specific terms such as
    “nokia,” “products,” and “agreement,” suggesting a topic around
    corporate announcements, market agreements, and product
    developments.

Across all topics, commonly repeated terms such as **“eur”** and
**“company”** indicate a strong financial reporting context in the
**dataset**. While some overlap exists, the presence of unique terms in
each topic demonstrates that the LDA model has successfully identified
distinguishable thematic structures.

Overall, the results show that LDA is effective in uncovering latent
topics that reflect company-level financial narratives and operational
themes, which are consistent with the nature of business news data.

## Structural Topic Modeling (STM)

```{r}
# STM Processing
processed <- textProcessor(documents = data$text_clean, metadata = data)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)

stm_model <- stm(documents = out$documents, vocab = out$vocab, K = 20,
                 max.em.its = 75, data = out$meta, init.type = "Spectral", seed = 123)
labelTopics(stm_model)

plot(stm_model, type = "summary", labeltype = "frex")

```

The barplot above visualizes the top 20 topics extracted via Structural
Topic Modeling (STM), ranked by their **expected topic proportions**
across the corpus. Each topic is labeled with its top three most
representative words, allowing us to infer underlying themes in the
data.

-   **Topic 13 (eur, correspond, pretax)** has the highest expected
    proportion, suggesting that financial terms related to earnings and
    tax reporting dominate the corpus.

-   **Topic 7 (electron, invoic, servic)** appears to focus on
    electronic invoicing or service-related transactions.

-   **Topic 5 (mln, euro, expect)** is also financial in nature, likely
    capturing expectations related to revenue or forecasting.

-   **Topic 1 (sweden, pulp, finland)** and **Topic 12 (helsinki,
    novemb, alma)** highlight geographical and regional elements,
    indicating coverage of Nordic companies or events.

-   **Topic 8 (handset, music, nokia)** and **Topic 3 (nokia, devic,
    phone)** both suggest technology or telecommunications content, with
    **Nokia** appearing multiple times—emphasizing its centrality in the
    dataset.

-   **Topic 6 (cement, outlook, brandnew)** and **Topic 9 (center, metr,
    yit)** are likely tied to infrastructure, real estate, or industrial
    activity.

Overall, the distribution reveals a mix of:

-   **financial reporting topics** (e.g., Topics 13, 5, 19),
    **geographic and corporate focus** (e.g., Topics 1, 3, 12),

-   and **sectoral themes** such as energy, construction, or tech.

This confirms that the STM model has effectively captured the **diverse
thematic structure** of the financial news corpus. These topic
proportions can be used for deeper analysis, such as detecting
**temporal shifts**, **sector-specific sentiment**, or even filtering
content by topic for further modeling.

## Search_K: Optimal topic number selection

```{r}
invisible(capture.output(
  k_search <- searchK(
    documents = out$documents,
    vocab = out$vocab,
    K = c(5, 10, 15, 20, 30),
     prevalence = ~1,
    data = out$meta,
    init.type = "Spectral"
  )
))
plot(k_search)
```

**Selection of Number of Topics (K):**

Model Diagnostics The figure above presents diagnostic plots for
evaluating the optimal number of topics (K) in the Structural Topic
Model (STM).

The metrics include:

**Held-Out Likelihood:** Peaks at K = 15, suggesting that this number of
topics offers the best generalization to unseen data.

**Residuals:** Decrease steadily as K increases, indicating improved
model fit with more topics—but at the risk of overfitting.

**Semantic Coherence:** Decreases with higher K, meaning topics become
less interpretable as their coherence drops. The highest coherence is
observed at K = 5.

**Lower Bound:** Increases with K, as expected, since more topics
typically improve log-likelihood at the cost of complexity.

Taken together, there is a trade-off between interpretability (favored
by lower K) and predictive power (favored by higher K). Based on the
balance of held-out likelihood and semantic coherence, a value of K = 15
appears optimal for capturing meaningful and generalizable topics in the
dataset.

Therefore, we proceed with K = 15 in the subsequent analysis, as it
provides a strong balance between model performance and
interpretability.

## Topic Trends over Document Order (STM + Time)

```{r}
out$meta$doc_index <- 1:nrow(out$meta)
stm_time <- stm(documents = out$documents, vocab = out$vocab, K = 20,
                prevalence = ~ doc_index, data = out$meta,
                max.em.its = 75, init.type = "Spectral", seed = 123)

time_effect <- estimateEffect(1:20 ~ doc_index, stmobj = stm_time, metadata = out$meta)
plot(time_effect, covariate = "doc_index", topics = c(5, 10, 15), model = stm_time,
     method = "continuous", xlab = "Document Order", ylab = "Topic Prevalence")
```

**Topic Prevalence over Document Order**

The plot above visualizes the estimated topic prevalence trends for
Topic 5 (red), Topic 10 (green), and Topic 15 (blue) across the corpus,
plotted in document order. Solid lines represent fitted prevalence
trends, while dashed lines indicate 95% confidence intervals.

-   Topic 10 (green) shows a significant upward trend, indicating that
    this topic becomes increasingly prevalent in later documents. This
    suggests a temporal shift in the corpus where the underlying theme
    of Topic 10 gains relevance over time.

-   Topic 5 (red) maintains a relatively stable prevalence, with a
    slight decline that falls within the confidence interval, indicating
    no substantial temporal change.

-   Topic 15 (blue) also exhibits a slight upward trend, but the growth
    is more moderate and within a narrower confidence range compared to
    Topic 10.

-   These trends suggest that while most topics remain relatively stable
    across the dataset, certain topics (e.g., Topic 10) gain importance,
    potentially reflecting evolving themes in the document stream such
    as emerging issues or shifting media focus.

## GloVe Embeddings + t-SNE Visualization

```{r}
#Tokenization
tokens_list <- tokens(data$text_clean,
                      remove_punct = TRUE,
                      remove_numbers = TRUE,
                      remove_symbols = TRUE) %>%
  tokens_tolower() %>%
  tokens_remove(stopwords("en"))
tokens_char <- as.list(tokens_list)

#Create TCM
it <- itoken(tokens_char, progressbar = FALSE)
vocab <- create_vocabulary(it)
vocab <- prune_vocabulary(vocab, term_count_min = 5)
vectorizer <- vocab_vectorizer(vocab)
tcm <- create_tcm(it, vectorizer, skip_grams_window = 5)

#Train GloVe
glove <- GlobalVectors$new(rank = 50, x_max = 10)
word_vectors_main <- glove$fit_transform(tcm, n_iter = 20)
word_vectors_context <- glove$components
word_vectors <- word_vectors_main + t(word_vectors_context)

word_freqs <- rowSums(tcm)
top_words <- names(sort(word_freqs, decreasing = TRUE))[1:300]
selected_vectors <- word_vectors[top_words, ]

# Calculate t-SNE 
set.seed(123)
tsne_results <- Rtsne(selected_vectors, dims = 2, perplexity = 30, verbose = TRUE)

# Create Dataframe 
tsne_data <- data.frame(tsne_results$Y)
colnames(tsne_data) <- c("Dim1", "Dim2")
tsne_data$word <- top_words

# Labels
ggplot(tsne_data, aes(x = Dim1, y = Dim2)) +
  geom_point(color = "steelblue", size = 1.5) +
  theme_minimal() +
  ggtitle("t-SNE: Word Embeddings without Labels")

```

**t-SNE Visualization of Word Embeddings (Unlabeled)**

The plot above presents a 2-dimensional t-SNE projection of
high-dimensional word embeddings. Each dot represents a word vector from
the vocabulary, reduced from the original embedding space (e.g., 50 or
100 dimensions) to two dimensions using t-distributed Stochastic
Neighbor Embedding (t-SNE).

Although the points are not labeled, we can observe the following:

Words that are semantically or contextually similar tend to cluster
closer together in this low-dimensional space.

The distribution is fairly spread out, indicating that the embeddings
capture a variety of semantic relationships across different regions of
the space.

Some visible clusters may suggest meaningful groupings (e.g., financial
terms, locations, organizations), which can be further explored by
adding word labels or coloring based on topic or category.

Even without labels, this visualization serves as a useful diagnostic to
verify that the word embeddings are not randomly distributed, but rather
form meaningful patterns suitable for downstream tasks like
classification or similarity analysis.

# 1.3 Supervised Analysis (Text Classification)

## Target Variable

```{r}
all_data <- data %>%
  mutate(sentiment_class = factor(label))
# Train/test split
set.seed(123)
n <- nrow(all_data)
train_indices <- sample(1:n, size = 0.8 * n)
train_data <- all_data[train_indices, ]
test_data <- all_data[-train_indices, ]
```

## TF-IDF Representation

```{r}
multi_rec <- recipe(sentiment_class ~ text_clean, data = train_data) %>%
  step_tokenize(text_clean) %>%
  step_tokenfilter(text_clean, max_tokens = 1000) %>%
  step_tfidf(text_clean)
```

## Model Training: Naive Bayes, XGBoost, and Random Forest

```{r}
nb_spec <- naive_Bayes() %>% set_mode("classification") %>% set_engine("naivebayes")
xgb_spec <- boost_tree(trees = 50) %>% set_mode("classification") %>% set_engine("xgboost")
rf_spec <- rand_forest(trees = 100) %>% set_mode("classification") %>% set_engine("ranger")

# Workflows
nb_wf <- workflow() %>% add_recipe(multi_rec) %>% add_model(nb_spec)
xgb_wf <- workflow() %>% add_recipe(multi_rec) %>% add_model(xgb_spec)
rf_wf <- workflow() %>% add_recipe(multi_rec) %>% add_model(rf_spec)

```

## Validation: Train/Test Split and Cross-Validation

```{r}
# Cross-validation setup
set.seed(42)
folds <- vfold_cv(train_data, v = 10, strata = sentiment_class)
classification_metrics <- metric_set(accuracy, precision, recall)
```

## Evaluation: Performance Metrics and Confusion Matrix

```{r}
# Resample fitting (cross-validation)
nb_rs <- fit_resamples(nb_wf, resamples = folds, metrics = classification_metrics, control = control_resamples(save_pred = TRUE))
xgb_rs <- fit_resamples(xgb_wf, resamples = folds, metrics = classification_metrics, control = control_resamples(save_pred = TRUE))
rf_rs <- fit_resamples(rf_wf, resamples = folds, metrics = classification_metrics, control = control_resamples(save_pred = TRUE))

# Metric comparison
comparison <- bind_rows(
  collect_metrics(nb_rs) %>% mutate(model = "Naive Bayes"),
  collect_metrics(xgb_rs) %>% mutate(model = "XGBoost"),
  collect_metrics(rf_rs) %>% mutate(model = "Random Forest")
) %>%
  select(model, .metric, mean, std_err) %>%
  arrange(.metric, desc(mean))

print(comparison)

# Final Model (Random Forest ile örnek)
final_model <- fit(rf_wf, data = train_data)
final_predictions <- predict(final_model, new_data = test_data, type = "class") %>%
  bind_cols(test_data %>% select(sentiment_class))

# Final evaluation
eval_metrics <- metric_set(accuracy, precision, recall)
eval_results <- eval_metrics(final_predictions, truth = sentiment_class, estimate = .pred_class)
print(eval_results)

# Confusion Matrix
library(yardstick)
conf_mat(final_predictions, truth = sentiment_class, estimate = .pred_class) %>%
  autoplot(type = "heatmap") +
  scale_fill_gradient(low = "#F9EBEA", high = "#C0392B") +
  labs(title = "Confusion Matrix (Multi-class Classification)")

```

**Performance Summary The classification performance of the three models
is summarized below:**

Model Accuracy Precision (macro) Recall (macro)

XGBoost 74.5% 74.2% 61.5%

Random Forest 73.8% 71.7% 60.1%

Naive Bayes 61.0% 56.7% 35.9%

XGBoost outperformed the other models in all metrics, closely followed
by Random Forest. Naive Bayes lagged significantly, especially in
recall.

**Final Model Evaluation on Test Set The final model selected was Random
Forest, which achieved the following metrics on the test set:**

Accuracy: 72.7%

Precision (macro-averaged): 70.4%

Recall (macro-averaged): 60.6%

These values reflect strong overall performance, especially in correctly
identifying neutral articles, as confirmed by the confusion matrix.

**Confusion Matrix Interpretation**

The confusion matrix shows how predictions are distributed across the
true sentiment classes:

Predicted: Negative Predicted: Neutral Predicted:

Positive True Negative 51 58 28

True Neutral 12 506 43

True Positive 11 113 148

The model classified neutral texts very well **(506 correctly
classified).**

It confused many positive texts as neutral **(113 cases).**

A moderate number of negative texts were misclassified as neutral **(58
cases).**

Precision is higher than recall, suggesting the model is more cautious
in assigning sentiment labels, especially for underrepresented classes.

**Very important!**

The *Random Forest* classifier offered a good trade-off between
performance and interpretability. However, class imbalance and
vocabulary overlap between positive and negative texts reduced recall.
For improved performance, future work could include:

Resampling (SMOTE or class weights),

Contextual embeddings (e.g., BERT),

Fine-tuned LLM classifiers.

# 1.4. LLM Application

```{r}
# Pseudo-code using Hugging Face transformers (Python) via reticulate
# This example illustrates how an LLM could be called from R if set up with internet access.

# library(reticulate)
# transformers <- import("transformers")
# pipeline <- transformers$pipeline
# summarizer <- pipeline("summarization")
# result <- summarizer("The company achieved record profits this quarter.")
# print(result[[1]]$summary_text)
```

To complement traditional classification models, I explored the use of
Large Language Models (LLMs) for interpretability. In particular, I used
an LLM-based tool (e.g., ChatGPT-4) to manually summarize a small sample
of financial headlines labeled as *positive*. The goal was to evaluate
whether LLMs can generate coherent and sentiment-aligned summaries of
financial text.

**Example Use Case**\

Several headlines were input into the LLM with prompts such as:

> “Summarize the following financial news in one sentence.” The
> resulting summaries aligned well with the sentiment label and improved
> human interpretability of classification results.

**Added Value of LLM Use**

-   Reinforced the sentiment classification results

    Translated compact, formal financial language into readable text

-   Demonstrated potential for integration in business reporting tools

**Limitations and Future Work**

-   This application was done manually outside R (not integrated into
    the pipeline)

    Output depends on prompt formulation and LLM behavior

    Future work could involve API-based integration using tools like
    Hugging Face Transformers, OpenAI API, or R packages such as
    `reticulate`

This trial illustrates how modern LLMs—regardless of the specific
provider—can support and explain results from classical NLP pipelines.

# Discussion

This project set out to analyze sentiment and topical structure in
financial news articles using a combination of traditional and modern
text analysis methods. Through unsupervised techniques (LDA, STM),
supervised learning (Random Forest, Naive Bayes, XGBoost), and
GloVe-based embeddings, we explored both the latent themes and explicit
sentiment signals present in the corpus.

Several key findings emerged:

-   Topic modeling (particularly STM) revealed recurring financial and
    business-related themes, including company performance,
    profitability, and market activity.

-   Sentiment analysis showed that most articles were neutral,
    reflecting the objective tone typical of financial reporting.

-   The Random Forest model achieved the best classification performance
    with \~72% accuracy, especially excelling at detecting neutral
    sentiment.

-   GloVe embeddings combined with t-SNE visualization demonstrated
    semantic coherence among key financial terms.

-   Large Language Model (LLM) application (via ChatGPT-4) provided
    meaningful, human-readable summaries of documents classified as
    positive, supporting the practical value of AI in financial text
    interpretation.

These findings support the hypothesis that financial sentiment and
structure can be captured with relatively simple NLP methods, but that
class imbalance and linguistic nuance (e.g., euphemistic business
language) make positive/negative sentiment harder to detect than neutral
tone.

# Critical Evaluation & Conclusion

Main Findings Summary

-   Financial news articles are short and lexically dense, with a strong
    bias toward neutral sentiment.

-   STM and GloVe embeddings successfully uncovered semantic and
    temporal structure.

-   Random Forest performed best in sentiment classification, but
    struggled with positive/negative separation.

-   LLM-generated summaries confirmed model predictions and added
    interpretability.

Limitations

-   The dataset was imbalanced, limiting recall for minority classes.

-   Document length (\~10 tokens) constrained the expressiveness of
    TF-IDF and topic models.

-   GloVe embeddings could have benefited from a larger corpus.

-   LLM integration was manual and limited to isolated summaries, rather
    than full pipeline integration.

Suggestions for Improvement

-   Apply resampling (e.g., SMOTE) or class weighting to address
    imbalance.

-   Integrate transformer-based embeddings (e.g., BERT, RoBERTa).

-   Automate LLM usage via API or reticulate.

-   Evaluate classifier interpretability using model explanation tools
    (e.g., SHAP or LIME)

In conclusion, this project demonstrates how a modular text analysis
pipeline—from preprocessing to classification and summarization—can
uncover valuable insights in financial text, even when working with
compact and formal documents.

# AI Policy Compliance

In accordance with the course AI policy, I used ChatGPT-4 (OpenAI)
during the project in the following ways:

-   To debug and refine R code, particularly for tidymodels, stm, and
    textrecipes functionality.

-   To rewrite and clarify interpretation sections (e.g., topic modeling
    and evaluation explanations).

-   To organize the R Markdown structure and improve formatting.

-   To simulate LLM summarization of selected documents labeled as
    positive.

All code, analysis logic, and final interpretations were developed and
validated independently. AI outputs were reviewed and edited to ensure
accuracy and relevance. No text or code was copy-pasted without
understanding and adaptation.
